---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(50)
```

[![Travis build status](https://travis-ci.org/malcolmbarrett/koanr.svg?branch=master)](https://travis-ci.org/malcolmbarrett/koanr)
[![AppVeyor Build Status](https://ci.appveyor.com/malcolmbarrett/koanr)](https://ci.appveyor.com/api/projects/status/github//malcolmbarrett/koanr/?branch=master&svg=true)

# koanr

`koanr` is (mostly) a data package containing the text for several of the more important Zen koan texts: The Gateless Gate (`gateless_gate`), The Blue Cliff Record (`blue_cliff_record`), The Record of the Transmission of the Light(`record_of_light`), and The Book of Equanimity(`book_of_equanimity`). `koanr` also includes functions for sampling (real) koans and generating (fake) koans.


## Example

Sample from an existing koan:

```{r koan, results='asis', message=FALSE}
library(koanr)
koan(collection = gateless_gate, case = 1)
```

Or generate a fake one:

```{r fake_koan, results='asis'}
fake_koan()
```
