---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(50)
```

[![Travis build status](https://travis-ci.org/malcolmbarrett/koanr.svg?branch=master)](https://travis-ci.org/malcolmbarrett/koanr)
[![AppVeyor Build status](https://ci.appveyor.com/api/projects/status/myfqx9fpr4fqcgom?svg=true)](https://ci.appveyor.com/project/malcolmbarrett/koanr)


# koanr

`koanr` is (mostly) a data package containing the text for several of the more important Zen koan texts: The Gateless Gate (`gateless_gate`), The Blue Cliff Record (`blue_cliff_record`), The Record of the Transmission of the Light(`record_of_light`), and The Book of Equanimity(`book_of_equanimity`). `koanr` also includes functions for sampling koans.

## Examples

Quickly access a koan:

```{r koan, message=FALSE}
library(koanr)
koan(collection = gateless_gate, case = 1)
```

Pick a random koan:

```{r koan_random, message=FALSE}
koan()
```


Quickly bind all four collections:

```{r collect_all, message=FALSE}
collect_koans()
```

